Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-20 paper/paper.tex
pass on abstract and intro

JavaScript (\js{}) is today one of the most popular programming
languages around~\cite{business-insider,stackify}, with penetration in
various segments including, web development, mobile, and, more
recently, the Internet of Things~(IoT)~\cite{simply-technologies}. The
interest of the community for the language encourages constant
improvements in its specification and implementations. It is natural
to expect that such improvements lead to sensible changes in engine
implementation. Even small changes can have high practical impact. For
example, in October 2014 a new attribute added to Array objects
resulted in the MS Outlook Calendar web app stop working under
Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.
Intuitively, developing reliable engines is difficult because
specifications are incomplete and evolve frequently.

Finding bugs in \js\ engines is an important problem given the range
of applications that could be affected with those
bugs. It\Comment{Finding bugs in \js\ engines} is also
challenging. For example, a test that passes in one engine could
legitimately fail in a different engine because of some undefined
behavior in the spec\footnote{These cases of undefined behavior can be
  localized by searching for the string ``implementation-dependent''
  in the ES6 spec document~\cite{ecmas262-spec}.}. As another example,
a test may fail because the engine does not fully implement some
feature. The publicly-available Kangax compatibility
table~\cite{kangax} relates \js\ features with the engines that
support them. To sum, it is often non-trivial to assess if a test
fails because of a bug or because of some other reason making test
automation more challenging.

%% when a bug is found in some engine a test case is created and added to
%% the regression suite. Those test inputs often check interesting
%% scenarios that could reveal bugs in different engine
%% implementations.

@@

\emph{Related Ideas.}  It is worth noting that Differential
Testing~\cite{Brumley-etal-ss07} (DT) has been applied in a variety of
contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
It has shown to be specially practical in scenarios where the
observation of difference gives a strong signal of a real problem. For
example, Mozilla runs JS files\footnote{These files are created with
  the grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
  ``compare\_jit'' from funfuzz.} against different configurations of
a given build of their \smonkey\ engine (\eg{}, trying to enable or
not eager JIT compilation). In that setting, test outcomes are
expected to be identical. Mozilla uses this approach since 2002 and
have been able to find over 270 bugs since
then~\cite{jsfunfuzz-at-mozilla}, including security
bugs. Cross-engine differential testing, in contrast, has not been
popularized to similar extent. One possible reason is that it is still
not practical to fully automate the technique. In contrast to other
applications of differential testing, a number of legitimate reasons
exist, other than a bug, for a test execution to manifest discrepancy
(see Table~\ref{tab:false-positives}). Recently, Patra and
Pradel~\cite{patra2016learning} explored the idea. They proposed a
language-agnostic fuzzer to find cross-browser HTML+JS
discrepancies. Their main contribution is analytical whereas our main
contribution is empirical--goal is to evaluate ability and cost of
simple diversity-aware approaches to find bugs in \js\ engines.

>>>>

JavaScript (\js{}) is today one of the most popular programming
languages around~\cite{business-insider,stackify}, with penetration in
various segments including, web development, mobile, and, more
recently, the Internet of Things~(IoT)~\cite{simply-technologies}. The
interest of the community for the language encourages constant
improvements in its specification and implementations. It is natural
to expect that such improvements lead to sensible changes in engine
implementation. In fact, even small changes can have high practical impact. For
example, in October 2014 a new attribute added to Array objects
resulted in the MS Outlook Calendar web app stop working under
Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.

Finding bugs in \js\ engines is an important problem given the range
of applications that could be affected with those
bugs. It\Comment{Finding bugs in \js\ engines} is also
challenging. For example, a test that passes in one engine could
legitimately fail in a different engine because of some undefined
behavior in the spec\footnote{These cases of undefined behavior can be
  localized by searching for the string ``implementation-dependent''
  in the ES6 spec document~\cite{ecmas262-spec}.}. As another example,
a test may fail because the engine does not fully implement some
feature. The publicly-available Kangax compatibility
table~\cite{kangax} relates \js\ features with the engines that
support them. To sum, it is often non-trivial to assess if a test
fails because of a bug or because of some other reason making test
automation more challenging. Intuitively, developing reliable engines
is difficult because specifications are intentionally incomplete--for
development flexibility--and evolve frequently.

@@

\emph{Related Ideas.}  It is worth noting that Differential
Testing~\cite{Brumley-etal-ss07} (DT) has been applied in a variety of
contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
It has shown to be specially practical in scenarios where the
observation of difference gives a strong signal of a real problem. For
example, Mozilla runs JS files\footnote{These files are created with
  the grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
  ``compare\_jit'' from funfuzz.} against different configurations of
a given build of their \smonkey\ engine (\eg{}, trying to enable or
not eager JIT compilation). As the same engine is used, test outcomes are
expected to be identical. Mozilla uses this approach since 2002 and
have been able to find over 270 bugs since
then~\cite{jsfunfuzz-at-mozilla}, including security
bugs. Cross-engine differential testing, in contrast, has not been
popularized to similar extent. One possible reason is that it is still
not practical to fully automate the technique. In contrast to other
applications of differential testing, a number of legitimate reasons
exist, other than a bug, for a test execution to manifest discrepancy
(see Table~\ref{tab:false-positives}). Recently, Patra and
Pradel~\cite{patra2016learning} explored the idea. They proposed a
language-agnostic fuzzer to find cross-browser HTML+JS
discrepancies. Their main contribution is analytical whereas our main
contribution is empirical--goal is to evaluate ability and cost of
simple diversity-aware approaches to find bugs in \js\ engines.
